XXXXX

### 2014-09-27 paper/paper1.tex
R-120-HANDLE-RDF-COLLECTIONS

>>>>

examples:

\begin{itemize}
	\item size of collection
	\item first / last element of list must be a specific RDF literal
	\item compare elements of collection
	\item are collections identical?
	\item actions on RDF lists: \url{http://www.snee.com/bobdc.blog/2014/04/rdf-lists-and-sparql.html}
	\item 2. list element equals ''
	\item Does the list have more than 10 elements?
\end{itemize}

constraint (SPIN):

retrieves the 2. item from the list (2. student of Jedi mentor Jinn)

function call (SPIN):

\begin{ex}
BIND ( :getListItem( ?list, "1"xsd:nonNegativeInteger ) AS ?listItem ) .
\end{ex}

function (SPIN):

\begin{ex}
:getListItem
    a spin:Function ; rdfs:subClassOf spin:Functions ;
    spin:constraint [
        rdf:type spl:Argument ;
        spl:predicate sp:arg1 ;
        spl:valueType rdf:List ;
        rdfs:comment "list" ; ] ;
    spin:constraint [
        rdf:type spl:Argument ;
        spl:predicate sp:arg2 ;
        spl:valueType xsd:nonNegativeInteger ;
        rdfs:comment "item position (starting with 0)" ; ] ;
    spin:body [
        a sp:SELECT ;
        sp:text """
            SELECT ?item
            WHERE {
                ?arg1 :contents/rdf:rest{?arg2}/rdf:first ?item } """ ; ] ;
    spin:returnType rdfs:Resource .
\end{ex}

data:

\begin{ex}
:Jinn :students 
     ( :Xanatos :Kenobi ) . 
\end{ex}

result:

\begin{ex}
:Kenobi
\end{ex}
